Growth of the South African Economy:\\An Empirical Evaluation

### 2014-08-06 Articles/Article_EcolEcon_2014/Paper2.Rnw
All articles now use the new loadPostProcessedData function.

<<LINEX_abg_traj_graph_REXS_UK_U, fig.pos="H", fig.align='center', fig.width=3, fig.height=3.5, fig.cap="UK LINEX trajectory for REXS with $u$.">>=
triPlot(data=fortify(REXS1960_Models$REXS1960$UK$linex$`iK+iL+iU`), grid_lines=5, x=alpha, y=beta, z=gamma, geom=geom_line, aes_string="colour = iYear + 1960")
@

@@

<<LINEX_abg_traj_graph_IST_UK_U, fig.pos="H", fig.align='center', fig.width=3, fig.height=3.5, fig.cap="UK LINEX trajectory for IST with $u$.">>=
triPlot(data=fortify(IST_Models$IST$UK$linex$`iK+iL+iU`), grid_lines=5, x=alpha, y=beta, z=gamma, geom=geom_line, aes_string="colour = iYear + 1960")
@

@@

<<LINEX_abg_traj_graph_Leeds_UK_U, fig.pos="H", fig.align='center', fig.width=3, fig.height=3.5, fig.cap="UK LINEX trajectory for Leeds with $u$.">>=
triPlot(data=fortify(Leeds_Models$Leeds$UK$linex$`iK+iL+iU`), grid_lines=5, x=alpha, y=beta, z=gamma, geom=geom_line, aes_string="colour = iYear + 1960")
@

>>>>

<<LINEX_abg_traj_graph_REXS_UK_U, fig.pos="H", fig.align='center', fig.width=3, fig.height=3.5, fig.cap="UK LINEX trajectory for REXS with $u$.">>=
REXS1960_Models <- loadPostProcessedData(Source = "REXS1960", kind = "models")
triPlot(data=fortify(REXS1960_Models$REXS1960$UK$linex$`iK+iL+iU`), grid_lines=5, x=alpha, y=beta, z=gamma, geom=geom_line, aes_string="colour = iYear + 1960")
@

@@

<<LINEX_abg_traj_graph_IST_UK_U, fig.pos="H", fig.align='center', fig.width=3, fig.height=3.5, fig.cap="UK LINEX trajectory for IST with $u$.">>=
IST_Models <- loadPostProcessedData(Source = "IST", kind = "models")
triPlot(data=fortify(IST_Models$IST$UK$linex$`iK+iL+iU`), grid_lines=5, x=alpha, y=beta, z=gamma, geom=geom_line, aes_string="colour = iYear + 1960")
@

@@

<<LINEX_abg_traj_graph_Leeds_UK_U, fig.pos="H", fig.align='center', fig.width=3, fig.height=3.5, fig.cap="UK LINEX trajectory for Leeds with $u$.">>=
Leeds_Models <- loadPostProcessedData(Source = "Leeds", kind = "models")
triPlot(data=fortify(Leeds_Models$Leeds$UK$linex$`iK+iL+iU`), grid_lines=5, x=alpha, y=beta, z=gamma, geom=geom_line, aes_string="colour = iYear + 1960")
@

### 2014-08-06 Articles/Article_EnerEcon_2014/EconGrowth2-GraphsOnly.Rnw
All articles now use the new loadPostProcessedData function.

# Load historical data
# In Rstudio, this paper is generated from it's directory, which is "Article".
# We need to define paths relative to the location of the paper. 
# Relative path to historical data from Article
historicalData <- Calvin # From the EconData package

# Load coefficients from all models in one large data frame
coeffs_df <- tbl_df(Calvin_Coeffs)
# Load fitted data from all models in one large data frame
fitted_df <- tbl_df(Calvin_Fitted)

# Load the original models.
oModels <- Calvin_Models

>>>>

# Load historical data
historicalData <- Calvin # From the EconData package
# Load coefficients from all models in one large data frame
coeffs_df <- loadPostProcessedData(Source = "Calvin", kind = "coeffs")
# Load fitted data from all models in one large data frame
fitted_df <- loadPostProcessedData(Source = "Calvin", kind = "fitted")
# Load the original models.
oModels <- loadPostProcessedData(Source = "Calvin", kind = "models")

### 2014-08-06 Articles/Article_EnerEcon_2014/EconGrowth2.Rnw
All articles now use the new loadPostProcessedData function.

<<data, include=FALSE>>=
# Load historical data
historicalData <- Calvin # From the EconData package
# Load coefficients from all models in one large data frame
coeffs_df <- tbl_df(Calvin_Coeffs)
# Load fitted data from all models in one large data frame
fitted_df <- tbl_df(Calvin_Fitted)

# Load the original models.
oModels <- Calvin_Models
@

>>>>

<<data, include=FALSE>>=
# Load historical data
historicalData <- Calvin # From the EconData package
# Load coefficients from all models in one large data frame
coeffs_df <- loadPostProcessedData(Source = "Calvin", kind = "coeffs")
# Load fitted data from all models in one large data frame
fitted_df <- loadPostProcessedData(Source = "Calvin", kind = "fitted")
# Load the original models.
oModels <- loadPostProcessedData(Source = "Calvin", kind = "models")
@

### 2014-08-06 Articles/Article_Heun_Warr_2014/EcolEcon_HeunWarr.Rnw
All articles now use the new loadPostProcessedData function.

<<data, include=FALSE, eval=TRUE>>=
# Load historical data
historicalData <- REXS # From the EconData package
# Load coefficients from all models in one large data frame
coeffs_df <- tbl_df(REXS_Coeffs)
# Load fitted data from all models in one large data frame
fitted_df <- tbl_df(REXS_Fitted)

# Load the original models.
oModels <- REXS_Models
@

>>>>

<<data, include=FALSE, eval=TRUE>>=
# Load historical data
historicalData <- REXS # From the EconData package
# Load coefficients from all models in one large data frame
coeffs_df <- loadPostProcessedData(Source = "REXS", kind = "coeffs")
# Load fitted data from all models in one large data frame
fitted_df <- loadPostProcessedData(Source = "REXS", kind = "fitted")
# Load the original models.
oModels <- loadPostProcessedData(Source = "REXS", kind = "models")
@

### 2014-08-06 Articles/Article_JAE_2014/ZAGrowth_JAE.Rnw
All articles now use the new loadPostProcessedData function.

# Load coefficients from all models in one large data frame
coeffs_df <- tbl_df(AllCoef)
coeffs_df_ZA <- subset(coeffs_df, subset=country=="ZA")
# Load fitted data from all models in one large data frame
fitted_df <- tbl_df(AllFitted)
fitted_df_ZA <- subset(fitted_df, subset=Country=="ZA")
# Load the original models.
oModels_ZA <- OrigModels$ZA
@

>>>>

# Load coefficients from all models in one large data frame
coeffs_df <- loadPostProcessedData(Source = "Calvin", kind = "coeffs")
coeffs_df_ZA <- subset(coeffs_df, subset=country=="ZA")
# Load fitted data from all models in one large data frame
fitted_df <- loadPostProcessedData(Source = "Calvin", kind = "fitted")
fitted_df_ZA <- subset(fitted_df, subset=Country=="ZA")
# Load the original models.
oModels <- loadPostProcessedData(Source = "Calvin", kind = "models")
oModels_ZA <- oModels$Calvin$ZA
@
